Drivers of sex differences in consumption (NAMCS)

### 2017-06-26 sex-difference/namcs.Rmd
small fixes

import::from(survey, svyglm)
import::from(survey, svydesign)
```

@@

```{r total_plot}
abx_totals %>%
  mutate_at(vars(total, se), function(x) x/1e6) %>%
  mutate(ci=se*1.96,
         ci_low=total-ci,
         ci_high=total+ci) %>%
  select(abx, sex, total, ci_low, ci_high) %>%
  gather('key', 'value', total:ci_high) %>%
  mutate(key=case_when(.$sex=='male' & .$key=='total' ~ 'x',
                       .$sex=='male' & .$key=='ci_low' ~ 'xmin',
                       .$sex=='male' & .$key=='ci_high' ~ 'xmax',
                       .$sex=='female' & .$key=='total' ~ 'y',
                       .$sex=='female' & .$key=='ci_low' ~ 'ymin',
                       .$sex=='female' & .$key=='ci_high' ~ 'ymax')) %>%
  select(-sex) %>%
  spread(key, value) %>%
  mutate(ymin=if_else(ymin<0, 0, ymin)) %>% # fix the negative ymin for moxi
  mutate(highlight=abx %in% c('nitro')) %>%
  ggplot(aes(x=x, xmin=xmin, xmax=xmax, y=y, ymin=ymin, ymax=ymax, label=abx, color=highlight)) +
  geom_abline(col='gray') + geom_abline(slope=1.21277, col='gray') +
  geom_point() + geom_errorbar() + geom_errorbarh() +
  scale_color_manual(values=c('black', 'red')) +
  geom_text(nudge_x=1, nudge_y=0.5) +
  scale_x_continuous(breaks=c(0, 5, 10), limits=c(0, 10)) + xlab('No. rx. for men (millions)') +
  scale_y_continuous(breaks=c(0, 5, 10), limits=c(0, 12)) + ylab('No. rx. for women (millions)') +
  coord_fixed() +
  theme_minimal()
```

>>>>

library(survey)
```

@@

```{r total_plot}
abx_totals %>%
  mutate_at(vars(total, se), function(x) x/1e6) %>%
  mutate(ci=se*1.96,
         ci_low=total-ci,
         ci_high=total+ci) %>%
  select(abx, sex, total, ci_low, ci_high) %>%
  gather('key', 'value', total:ci_high) %>%
  mutate(key=case_when(.$sex=='male' & .$key=='total' ~ 'x',
                       .$sex=='male' & .$key=='ci_low' ~ 'xmin',
                       .$sex=='male' & .$key=='ci_high' ~ 'xmax',
                       .$sex=='female' & .$key=='total' ~ 'y',
                       .$sex=='female' & .$key=='ci_low' ~ 'ymin',
                       .$sex=='female' & .$key=='ci_high' ~ 'ymax')) %>%
  select(-sex) %>%
  spread(key, value) %>%
  mutate(ymin=if_else(ymin<0, 0, ymin)) %>% # fix the negative ymin for moxi
  mutate(highlight=abx %in% c('nitro', 'amox', 'amoxclav')) %>%
  ggplot(aes(x=x, xmin=xmin, xmax=xmax, y=y, ymin=ymin, ymax=ymax, label=abx, color=highlight)) +
  geom_abline(col='gray') + geom_abline(slope=1.21277, col='gray') +
  geom_point() + geom_errorbar() + geom_errorbarh() +
  scale_color_manual(values=c('black', 'red')) +
  geom_text(nudge_x=1, nudge_y=0.5) +
  scale_x_continuous(breaks=c(0, 5, 10), limits=c(0, 10)) + xlab('No. rx. for men (millions)') +
  scale_y_continuous(breaks=c(0, 5, 10), limits=c(0, 12)) + ylab('No. rx. for women (millions)') +
  coord_fixed() +
  theme_minimal()
```
